How demand pattern identification and multicriteria ABC classification can guide management decisions

### 2024-01-02 manuscript/FCPCOM/manuscript.tex
small changes

\begin{tabular}[l]{p{0.4cm} | p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} | p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm}}
 \multicolumn{1}{l}{} & \multicolumn{14}{l}{car mechanics company} \\
\cline {2-15} \\

@@

\cline {2-15} \\
 & \multicolumn{14}{l}{furniture trades company} \\
\cline {2-15} \\

@@

\cline {2-15} \\
 & \multicolumn{14}{l}{plastic packaging manufacturing company} \\
\cline {2-15} \\

@@

As we can see in this table, the pairwise comparison weights are adjusted primarily according to the  weights assigned to the first three criteria. Thus, although there is a change in the pairwise comparison weights, which may be significant, the weights assigned to the first three criteria will be preserved. The change will be made in the weights of the other criteria in order to force the consistency of the pairwise comparisons matrix. Another important point to note in the method is that the algorithm stops when the desired consistency rate is reached. So, it is more likely that there will be significant changes in the fourth criterion and the next ones. Therefore, it is important that the criteria are ordered in such a way that the three most relevant criteria for the company are among the first. Then the next most relevant criteria can be ordered from last to fourth position.

\subsection{Analysis of the ABC multicriterio classification}

@@

\end{tabular}
\caption{Multicriteria ABC and demand pattern classifications for three companies (results found by COPSolver)}
\label{tab:results}
\end{small}
\end{center}
\end{table}

>>>>

\begin{tabular}[l]{p{0.4cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} | p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm} p{0.5cm}}
\multicolumn{14}{l}{car mechanics company} \\
\cline {1-15} \\

@@

\cline {1-15} \\
\multicolumn{14}{l}{furniture trades company} \\
\cline {1-15} \\

@@

\cline {1-15} \\
\multicolumn{14}{l}{plastic packaging manufacturing company} \\
\cline {1-15} \\

@@

As we can see in this table, the pairwise comparison weights are adjusted primarily according to the  weights assigned to the first three criteria. Thus, although there is a change in the pairwise comparison weights, which may be significant, the weights assigned to the first three criteria will be preserved. The change will be made in the weights of the other criteria in order to force the consistency of the pairwise comparisons matrix. Another important point to note is that the algorithm stops when the desired consistency rate is reached. So, it is more likely that there will be significant changes in the fourth criterion and the next ones. Therefore, it is important that the criteria are ordered in such a way that the three most relevant criteria for the company are among the first. Then the next most relevant criteria can be ordered from last to fourth position.

\subsection{Analysis of the ABC multicriteria classification}

@@

\end{tabular}
\caption{ABC multicriteria and demand pattern classifications for three companies (results found by COPSolver)}
\label{tab:results}
\end{small}
\end{center}
\end{table}
